---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# catfacts

<!-- badges: start -->
<!-- badges: end -->

The goal of catfacts is to demonstrate an opinionated approach to structuring a shiny app. Primary motivation for catfacts is to avoid mistakes I have made in the past while developing. Key topics are:

* Handling and organizing data
* Documenting and controlling dependencies
* Testing with `expect_` functions from `testthat`

## Structure

```{r, echo=FALSE, comment=""}
fs::dir_tree(recurse = 2)
```

## Handling and organizing data

* **Problem:** I have a vector of 10 choices and that vector is copied/pasted throughout the app and the apps tests. Any changes to that dropdowns choices will require numerous, redundant changes.

* **Resolution:** Consider any static, reusable data and document it's creation in `data-raw`, save it in `data`. If the data comes from an external source, store the original in `inst/extdata`, document any manipulation in `data-raw` and save it in `data`. Reuse that data throughout the app and the apps tests.

## Documenting and controlling dependencies

* **Problem:** I just updated a package to use a development version which in turn broke a different app that depended on the CRAN version.

* **Solution:** Use `renv` to control project specific dependencies. I have never actually run into the problem I described but the thought of project specific dependencies makes me happy and less nervous about things breaking.

## Testing with `expect_` functions from `testthat`

* **Problem:** My data is dynamic and I want my tests to introduce randomness when possible, the snapshot approach using `shinytest` will not work.

* **Solution:** Use `shinytest` for automating the app operations and `testthat` for testing the apps output.

Note: `shinytest` does have a solution for handling dynamic data which is to use dummy data while in test mode, see [here](https://rstudio.github.io/shinytest/articles/in-depth.html#dealing-with-dynamic-data). However, to my knowledge `shinytest` cannot introduce randomness by design, only control it, see [here](https://rstudio.github.io/shinytest/articles/in-depth.html#controlling-randomness). 

For my particular use case, a user can generate many different outputs by selecting values from numerous dropdowns. My main concern is that regardless of what they pick, the output makes sense. As a result, I prefer a set of tests that randomly pick certain values from dropdowns and compare the actual result to the expected result with `expect_` functions from `testthat`.
